---
title: "README"
output: html_document
---
 # Purpose
 
 The purpose of this README is to document my thinking during the Data Science practical assesment. 
 
 First I would like to clear my environment and load my packages.
```{r}
rm(list = ls())
gc()
library(tidyverse)
library(ggthemes)
source(file = "code/read_all_rows.R")
```
 
 # Question 1
 
First, I read in the data that I'll be using for this question.
```{r}
movie_data <- read_csv("data/Movies/Movies.csv")
```
 
 Then for the first bullet we want to test whether a movie with a >80% rating from Rotten Tomatoes always has an audience rating of above 85%.
```{r }
# Wrangle the data so that its easier to use
rt_plot_data <- movie_data %>% rename(RT = "Rotten Tomatoes %") %>% rename(AR = "Audience  score %") %>% 
    select(c(Film, RT, AR)) %>% mutate(big_RT = ifelse(RT >= 80, 1, 0))

# Now we plot the data
rt_plot_data %>% 
    ggplot() +
    geom_histogram(aes(x = fct_reorder(Film, AR), y = AR, fill = big_RT), stat = "identity") +
    geom_hline(aes(yintercept = 85), color = "darkred", alpha = 0.6) +
    labs(title = "Audience Score by Film", subtitle = "Audience score per film differentiated by whether Rotten Tomatoes rated greater than 80%" ,x = "", y = "Audience Score")

```
 
As we can see there were a few movies 
 
For the second part of question 1 we will compare the profits of Disney films to other studios.
```{r}
# Again, we wrangle the data into a more useable format
dis_data <- movie_data %>% select(c(Film, "Lead Studio", Profitability)) %>% 
    rename(LS = "Lead Studio") %>% mutate(Disney = ifelse(LS == "Disney", 1, 0))

# Then we graph the data
dis_data %>% 
    ggplot() +
    geom_histogram(aes(x = fct_reorder(Film, Profitability), y = Profitability, fill = Disney), stat = "identity") +
    labs(x = "", y = "Profitability", title = "Relative Profitability of Disney Films")
```

 Disney has the second most profitable film but it by no means dominates the field in terms of profitability.
 
 The third part of the question (time is up for this for now)
```{r}

```
 
# Question 2

I have made a function that reads in the csv files and binds them by row.
```{r}
forbes_data <- read_all_rows(folder = "data/Forbes/")
```

After reading in the data, I see that the Net Worth column contains both numbers and letters. I would like to use only numerics.
```{r}
# First rangle the data, specifically cleaning the NetWorth column
forbes_clean <- forbes_data %>% mutate(NetWorth = gsub(" B", "", NetWorth)) %>% 
    mutate(NetWorth = as.numeric(gsub("^.{0,1}", "", NetWorth)))  
# make a dataframe for SA
SA <- forbes_clean %>% filter(Country == "South Africa")
#Graphing the data here. I am thinking of using points
SA %>% 
    ggplot() +
    geom_point(aes(x = Age, y = NetWorth, color = Name), size = 5) +
    geom_text(aes(x = Age, y = NetWorth, label = Name)) +
    labs(title = "South Africans in th Forbes List", subtitle = "A graph of net worth by age", x = "", y = "Net Worth") +
    theme_economist() +
    guides(color = F)

```

The second graph I want to draw for question two is the top 20 richest people on the Forbes list.
```{r}
top_20_rich <- forbes_clean %>% mutate(top_20 = ifelse(Rank <= 20, 1, 0)) %>% filter(top_20 == 1)

top_20_rich %>% 
    ggplot() + 
    geom_point(aes(x = fct_reorder(Name, Rank), y = Age, size = NetWorth, color = Industry)) +
    geom_text(aes(x = fct_reorder(Name, Rank), y = Age, label = Source)) +
    labs(title = "20 richest People on Earth", subtitle = "The world's richest arranged by net worth and age", x = "", caption = "Forbes") +
    theme_economist() +
    theme(axis.text.x=element_text(angle = 90, hjust = 1)) +
    guides(size = F)
    

```

# Question 3

Question three is the texevier question. I will start by reading in the data using a function that I created.
```{r}
tweet_data <- read_all_rds(folder = "data/Tweets/")
```

Now that I have the data loaded in, I can start to wrangle it a bit keeping in mind that we want to compare the media usage of each outlet
```{r}
tweet_data %>% mutate(username = ifelse("theeconomist", "The Economist", ifelse("cnnbrk", "CNN", "BBC"))) %>% select(c(date, username, video, picture)) %>% 
    gsub("^.{0,1}", "", NetWorth)
    summarise(across(c(ladder, ends_with("whisker")),
    list(median), .names = "{col}") )
```

